---
title: "Data analysis: Multiple imputation"
author: "MS"
date: "22/09/2021"
output: html_document
---

IMPORTANT: The original dataset collected information about university name which was then paired with a world rank. Both of these variables could be used to identify participants at institutions which, at the time, did not tie on ranks with any other institutions. Because of this, the variables were removed from the dataset. 

The variable `world_rank` was replaced with a randomly generated variable that correlated with the original rank with r = 0.9. Therefore the code below will still be able to run, however please note that any computations that use `world_rank` will not be exactly reproducible. 

The main analysis in the file `analysis_models.Rmd` uses the actual data that was used to fit the models reported in the manuscript. The statistical models used a categorical version of the variable (`world_rank` split into 4 levels), which doesn't pose risk of de-identification and was therefore retained. Basically, the statistical models `analysis_models.Rmd` can be reproduced exactly, but not the imputation. 


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

library(brms)
library(dplyr)
library(ggplot2)
library(magrittr)
library(mice)

source("../scripts/helpers.R")

data <- readRDS("../data/processed_data/stats_practice_processed_data_081221_world_rank_deidentified.rds")

```


Remove cases that are not going to included in the models and only summarised descriptively: 

- Forensic psychologists
- Industry scientists 
- Postgraduate taught students (these should not have participated in the first place but somehow slipped through). 

```{r}
model_data <- data %>% 
  dplyr::filter(ri_subfield != "Forensic psychology" | is.na(ri_subfield), 
                demo_level != "Postgraduate taught student" | is.na(demo_level), 
                demo_level != "Undergraduate taught student" | is.na(demo_level), 
                world_rank != -999 | is.na(world_rank)) %>% 
  dplyr::mutate(
    demo_level = droplevels(demo_level), 
    ri_subfield = droplevels(ri_subfield)
  )
```

# Compute outcomes 

```{r}
model_data %<>% 
  dplyr::mutate(
    # stats knowledge: 
    tf_overall_mean = rowMeans(select(., contains("tf_"))), 
    tf_norm_mean    = rowMeans(select(., contains("tf_norm"))), 
    tf_het_mean     = rowMeans(select(., contains("tf_het"))), 
    tf_lin_mean     = rowMeans(select(., contains("tf_lin"))), 
    tf_ind_mean     = rowMeans(select(., contains("tf_ind"))), 
    tf_out_inf_mean = rowMeans(select(., contains("tf_out_inf"))),
    
    # stats practice
    
    s1_check_sum = rowSums(select(., c(s1_check_num_out, s1_check_num_inf, s1_check_num_het, 
                                       s1_check_num_norm_sam,
                                       s1_check_num_norm_err))), 
    s2_check_sum = rowSums(select(., c(s2_check_num_out, s2_check_num_inf, s2_check_num_het, 
                                       s2_check_num_norm_sam,
                                       s2_check_num_norm_err)))
    
  )


```



# Imputation 

## Set up passive imputation 

```{r}
pred_method <- mice::make.method(model_data)
pred_method[] <- "pmm"
pred_method[index(model_data, "tf_norm_1"): index(model_data, "tf_out_inf_50")] <- ""
pred_method[index(model_data, "tf_overall_mean"): index(model_data, "tf_out_inf_mean")] <- ""
pred_method[c("id")] <- ""

# stats practice

pred_method["s1_check_sum"] <-  "~I(s1_check_num_out + s1_check_num_inf + s1_check_num_het + s1_check_num_norm_sam + s1_check_num_norm_err)"

pred_method["s2_check_sum"] <- "~I(s2_check_num_out + s2_check_num_inf + s2_check_num_het + s2_check_num_norm_sam + s2_check_num_norm_err)"

```


## Set up predictor matrix 

```{r}
default_cor <- 0.25
n_var = ncol(model_data)
mincor = c(rep(default_cor, times = n_var))


mincor[index(model_data, "ri_subfield")] <- 0.15

mincor[index(model_data, "s1_check_num_lin"):index(model_data, "s2_check_num_norm_err")] <- 1



pred <- mice::quickpred(data = model_data, 
                        mincor = mincor, 
                        minpuc = 0,
                        method = "spearman" , 
                        exclude = "id"
                        )

pred_df <- as.data.frame(pred)
```


#### Matrix adjustments


No predictions across assumptions 

```{r}
# as ~ assumption_string
as <- c(
  "contains('plot')", # 1
  "contains('out')",  # 2 
  "contains('inf')",  # 3
  "contains('norm')", # 4
  "contains('het')",  # 5
  "contains('lin')",  # 6
  "contains('ind')"   # 7
)

```

```{r}
# outliers shouldn't predict other categories: 
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_col = list(as[2]),
                                    dplyr_select_query_row = list(as[3], as[4], as[5], as[6], as[7]),
                                    assign = 0) 

# outliers should not be predicted by other categories (swap _row and _col args):
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[2]),
                                    dplyr_select_query_col = list(as[3], as[4], as[5], as[6], as[7]),
                                    assign = 0)


# influential cases shouldn't predict other categories: 
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_col = list(as[3]),
                                    dplyr_select_query_row = list(as[2], as[4], as[5], as[6], as[7]),
                                    assign = 0) 

# influential cases should not be predicted by other categories (swap _row and _col args):
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[3]),
                                    dplyr_select_query_col = list(as[2], as[4], as[5], as[6], as[7]),
                                    assign = 0) 

# normality shouldn't predict other categories: 
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_col = list(as[4]),
                                    dplyr_select_query_row = list(as[2], as[3], as[5], as[6], as[7]),
                                    assign = 0) 

# normality should not be predicted by other categories (swap _row and _col args):
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[4]),
                                    dplyr_select_query_col = list(as[2], as[3], as[5], as[6], as[7]),
                                    assign = 0) 

# het shouldn't predict other categories: 
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_col = list(as[5]),
                                    dplyr_select_query_row = list(as[2], as[3], as[4], as[6], as[7]),
                                    assign = 0) 

# het should not be predicted by other categories (swap _row and _col args):
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[5]),
                                    dplyr_select_query_col = list(as[2], as[3], as[4], as[6], as[7]),
                                    assign = 0) 

# linearity shouldn't predict other categories: 
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_col = list(as[6]),
                                    dplyr_select_query_row = list(as[2], as[3], as[4], as[5], as[7]),
                                    assign = 0) 

# linearity should not be predicted by other categories (swap _row and _col args):
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[6]),
                                    dplyr_select_query_col = list(as[2], as[3], as[4], as[5], as[7]),
                                    assign = 0) 


# independence
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[7]),
                                    dplyr_select_query_col = list(as[2], as[3], as[4], as[5], as[6]),
                                    assign = 0) 

pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df, 
                                    dplyr_select_query_row = list(as[7]),
                                    dplyr_select_query_col = list(as[2], as[3], as[4], as[5], as[6]),
                                    assign = 0) 
```



#### stepwise predictor selection


```{r}
get_formula <- function(data = imputed_data, variable){
  formula_unfolded <- paste0(data$formulas[variable][[1]]) 
  formula_unfolded[3] %<>% stringr::str_replace(., pattern = "0", replacement = "1")
  formula <- paste0(formula_unfolded[2], formula_unfolded[1], formula_unfolded[3])
  as.formula(formula)
}

get_predictors <- function(stepwise_model){
  preds_stringr <- 
    stepwise_model$call$formula[[3]] %>% 
    toString() %>% 
    stringr::str_remove_all(., "[+,]") %>% 
    stringr::str_split(., pattern = " ")
  
  preds <- preds_stringr[[1]][!preds_stringr[[1]] %in% c("", "-", "1")]
  return(preds)
}
```

```{r}
data_to_use <- na.exclude(model_data)
```

s1_check_num_norm_sam

```{r}
#imputed_data$formulas$s1_check_num_norm_sam

s1_check_num_norm_sam_mod <- lm(
  s1_check_num_norm_sam ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_norm_1 + tf_norm_2 + tf_norm_3 + tf_norm_4 + 
    tf_norm_5 + tf_norm_6 + tf_norm_7 + tf_norm_8 + tf_norm_9 + 
    tf_norm_10 + 
    
    s1_selected_relevant_norm_sam + s2_selected_relevant_norm_sam + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 
    
    s2_check_num_norm_sam + s1_n_check_norm_sam + s2_n_check_norm_sam + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_norm_sam_mod_step <- MASS::stepAIC(s1_check_num_norm_sam_mod, direction = "backward", 
                    trace = FALSE)


s1_check_num_norm_sam_preds <- get_predictors(s1_check_num_norm_sam_mod_step)
s1_check_num_norm_sam_preds
```

s2_check_num_norm_sam

```{r}
#imputed_data$formulas$s1_check_num_norm_sam

s2_check_num_norm_sam_mod <- lm(
  s2_check_num_norm_sam ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_norm_1 + tf_norm_2 + tf_norm_3 + tf_norm_4 + 
    tf_norm_5 + tf_norm_6 + tf_norm_7 + tf_norm_8 + tf_norm_9 + 
    tf_norm_10 + 
    
    s1_selected_relevant_norm_sam + s2_selected_relevant_norm_sam + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 
    
    s1_check_num_norm_sam + s1_check_num_norm_err + 
    s2_check_num_norm_err + s1_n_check_norm_sam + s2_n_check_norm_sam + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_norm_sam_mod_step <- MASS::stepAIC(s2_check_num_norm_sam_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_norm_sam_preds <- get_predictors(s2_check_num_norm_sam_mod_step)
s2_check_num_norm_sam_preds
```


s1_check_num_norm_err

```{r}

s1_check_num_norm_err_mod <- lm(
  s1_check_num_norm_err ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_norm_1 + tf_norm_2 + tf_norm_3 + tf_norm_4 + 
    tf_norm_5 + tf_norm_6 + tf_norm_7 + tf_norm_8 + tf_norm_9 + 
    tf_norm_10 + 
    
    s1_selected_relevant_norm_err + s2_selected_relevant_norm_err + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 
    
    s2_check_num_norm_err + s1_n_check_norm_err + s2_n_check_norm_err + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_norm_err_mod_step <- MASS::stepAIC(s1_check_num_norm_err_mod, direction = "backward", 
                    trace = FALSE)


s1_check_num_norm_err_preds <- get_predictors(s1_check_num_norm_err_mod_step)
s1_check_num_norm_err_preds

data_to_use
```



s2_check_num_norm_sam

```{r}
#imputed_data$formulas$s2_check_num_norm_err

s2_check_num_norm_err_mod <- lm(
  s2_check_num_norm_err ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_norm_1 + tf_norm_2 + tf_norm_3 + tf_norm_4 + 
    tf_norm_5 + tf_norm_6 + tf_norm_7 + tf_norm_8 + tf_norm_9 + 
    tf_norm_10 + 
    
    s1_selected_relevant_norm_err + s2_selected_relevant_norm_err + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 
    
    s1_check_num_norm_err + s1_n_check_norm_sam + s2_n_check_norm_sam + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_norm_err_mod_step <- MASS::stepAIC(s2_check_num_norm_err_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_norm_err_preds <- get_predictors(s2_check_num_norm_err_mod_step)
s2_check_num_norm_err_preds
```


s1_check_num_het

```{r}
#imputed_data$formulas$s1_check_num_het

s1_check_num_het_mod <- lm(
  s1_check_num_het ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_het_11 + tf_het_12 + tf_het_13 + tf_het_14 + 
    tf_het_15 + tf_het_16 + tf_het_17 + tf_het_18 + tf_het_19 + 
    tf_het_20 + 
    
    s1_selected_relevant_het + s2_selected_relevant_het + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s2_check_num_het + s1_n_check_het + s2_n_check_het + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_het_mod_step <- MASS::stepAIC(s1_check_num_het_mod, direction = "backward", 
                    trace = FALSE)


s1_check_num_het_preds <- get_predictors(s1_check_num_het_mod_step)
s1_check_num_het_preds
```



s2_check_num_het

```{r}
#imputed_data$formulas$s2_check_num_het

s2_check_num_het_mod <- lm(
  s2_check_num_het ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_het_11 + tf_het_12 + tf_het_13 + tf_het_14 + 
    tf_het_15 + tf_het_16 + tf_het_17 + tf_het_18 + tf_het_19 + 
    tf_het_20 +
    
    s1_selected_relevant_het + s2_selected_relevant_het + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s1_check_num_het + s1_n_check_het + s2_n_check_het + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_het_mod_step <- MASS::stepAIC(s2_check_num_het_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_het_preds <- get_predictors(s2_check_num_het_mod_step)
s2_check_num_het_preds
```


s1_check_num_lin

```{r}
#imputed_data$formulas$s1_check_num_lin

s1_check_num_lin_mod <- lm(
  s1_check_num_lin ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_lin_21 + tf_lin_22 + tf_lin_23 + tf_lin_24 + 
    tf_lin_25 + tf_lin_26 + tf_lin_27 + tf_lin_28 + tf_lin_29 + 
    tf_lin_30 +
    
    s1_selected_relevant_lin + s2_selected_relevant_lin + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s2_check_num_lin + s1_n_check_lin + s2_n_check_lin + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_lin_mod_step <- MASS::stepAIC(s1_check_num_lin_mod, direction = "backward", 
                    trace = FALSE)


s1_check_num_lin_preds <- get_predictors(s1_check_num_lin_mod_step)
s1_check_num_lin_preds
```



s2_check_num_lin

```{r}
#imputed_data$formulas$s2_check_num_lin

s2_check_num_lin_mod <- lm(
  s2_check_num_lin ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_lin_21 + tf_lin_22 + tf_lin_23 + tf_lin_24 + 
    tf_lin_25 + tf_lin_26 + tf_lin_27 + tf_lin_28 + tf_lin_29 + 
    tf_lin_30 +
    
    s1_selected_relevant_lin + s2_selected_relevant_lin + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s1_check_num_lin + s1_n_check_lin + s2_n_check_lin + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_lin_mod_step <- MASS::stepAIC(s2_check_num_lin_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_lin_preds <- get_predictors(s2_check_num_lin_mod_step)
s2_check_num_lin_preds
```

s1_check_num_ind

```{r}
#imputed_data$formulas$s1_check_num_ind

s1_check_num_ind_mod <- lm(
  s1_check_num_ind ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_ind_31 + tf_ind_32 + tf_ind_33 + tf_ind_34 + 
    tf_ind_35 + tf_ind_36 + tf_ind_37 + tf_ind_38 + tf_ind_39 + 
    tf_ind_40 +
    
    s1_selected_relevant_ind + s2_selected_relevant_ind + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s2_check_num_ind + s1_n_check_ind + s2_n_check_ind + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_ind_mod_step <- MASS::stepAIC(s1_check_num_ind_mod, direction = "backward", 
                    trace = FALSE)


s1_check_num_ind_preds <- get_predictors(s1_check_num_ind_mod_step)
s1_check_num_ind_preds
```



s2_check_num_ind

```{r}
#imputed_data$formulas$s2_check_num_ind

s2_check_num_ind_mod <- lm(
  s2_check_num_ind ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_ind_31 + tf_ind_32 + tf_ind_33 + tf_ind_34 + 
    tf_ind_35 + tf_ind_36 + tf_ind_37 + tf_ind_38 + tf_ind_39 + 
    tf_ind_40 +
    
    s1_selected_relevant_ind + s2_selected_relevant_ind + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s1_check_num_ind + s1_n_check_ind + s2_n_check_ind + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_ind_mod_step <- MASS::stepAIC(s2_check_num_ind_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_ind_preds <- get_predictors(s2_check_num_ind_mod_step)
s2_check_num_ind_preds
```


s1_check_num_out

```{r}
#imputed_data$formulas$s1_check_num_out

s1_check_num_out_mod <- lm(
  s1_check_num_out ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_out_inf_41 + tf_out_inf_42 + tf_out_inf_43 + 
    tf_out_inf_44 + tf_out_inf_45 + tf_out_inf_46 + tf_out_inf_47 + 
    tf_out_inf_48 + tf_out_inf_49 + tf_out_inf_50 +
    
    s1_selected_relevant_out + s2_selected_relevant_out + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s2_check_num_out + s1_n_check_out + s2_n_check_out + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_out_mod_step <- MASS::stepAIC(s1_check_num_out_mod, direction = "backward", 
                    trace = FALSE)


s1_check_num_out_preds <- get_predictors(s1_check_num_out_mod_step)
s1_check_num_out_preds
```



s2_check_num_out

```{r}
#imputed_data$formulas$s2_check_num_out

s2_check_num_out_mod <- lm(
  s2_check_num_out ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_out_inf_41 + tf_out_inf_42 + tf_out_inf_43 + 
    tf_out_inf_44 + tf_out_inf_45 + tf_out_inf_46 + tf_out_inf_47 + 
    tf_out_inf_48 + tf_out_inf_49 + tf_out_inf_50 +
    
    s1_selected_relevant_out + s2_selected_relevant_out + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s1_check_num_out + s1_n_check_out + s2_n_check_out + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_out_mod_step <- MASS::stepAIC(s2_check_num_out_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_out_preds <- get_predictors(s2_check_num_out_mod_step)
s2_check_num_out_preds
```


s1_check_num_inf

```{r}
#imputed_data$formulas$s1_check_num_inf

s1_check_num_inf_mod <- lm(
  s1_check_num_inf ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_out_inf_41 + tf_out_inf_42 + tf_out_inf_43 + 
    tf_out_inf_44 + tf_out_inf_45 + tf_out_inf_46 + tf_out_inf_47 + 
    tf_out_inf_48 + tf_out_inf_49 + tf_out_inf_50 +
    
    s1_selected_relevant_inf + s2_selected_relevant_inf + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s2_check_num_inf + s1_n_check_inf + s2_n_check_inf + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s2_check_sum,
  data = data_to_use,
)

s1_check_num_inf_mod_step <- MASS::stepAIC(s1_check_num_inf_mod, direction = "backward", 
                    trace = FALSE)

s1_check_num_inf_preds <- get_predictors(s1_check_num_inf_mod_step)
s1_check_num_inf_preds
```



s2_check_num_inf

```{r}
#imputed_data$formulas$s2_check_num_inf

s2_check_num_inf_mod <- lm(
  s2_check_num_inf ~ 1 + 
    ri_teach + ri_subfield + recruitment + world_rank + 
    demo_level + ri_preferred_ht + 
    
    tf_out_inf_41 + tf_out_inf_42 + tf_out_inf_43 + 
    tf_out_inf_44 + tf_out_inf_45 + tf_out_inf_46 + tf_out_inf_47 + 
    tf_out_inf_48 + tf_out_inf_49 + tf_out_inf_50 +
    
    s1_selected_relevant_inf + s2_selected_relevant_inf + 
    s1_selected_relevant_dontknow + s2_selected_relevant_dontknow + 

    s1_check_num_inf + s1_n_check_inf + s2_n_check_inf + 
    
    methods_select_1 + methods_select_2 + methods_select_3 + 
    methods_select_4 + methods_select_5 + methods_select_6 + 
    methods_select_7 + methods_select_8 + methods_select_9 + 
    methods_select_10 + methods_select_11 + methods_select_12 + 
    methods_select_13 + methods_select_14 + methods_select_15 + 
    methods_select_16 + methods_select_17 + methods_select_18 + 
    methods_select_19 + methods_select_20 + methods_select_21 + 
    methods_select_22 + methods_select_23 + methods_select_24 + 
    
    rank_cat + 
    
    s1_check_sum,
  data = data_to_use,
)

s2_check_num_inf_mod_step <- MASS::stepAIC(s2_check_num_inf_mod, direction = "backward", 
                    trace = FALSE)


s2_check_num_inf_preds <- get_predictors(s2_check_num_inf_mod_step)
s2_check_num_inf_preds
```


regression selected variables

```{r}
pred_df["s1_check_num_norm_sam", s1_check_num_norm_sam_preds] <- 1
pred_df["s2_check_num_norm_sam", s2_check_num_norm_sam_preds] <- 1

pred_df["s1_check_num_norm_err", s1_check_num_norm_err_preds] <- 1
pred_df["s2_check_num_norm_err", s2_check_num_norm_err_preds] <- 1

pred_df["s1_check_num_het", s1_check_num_het_preds] <- 1
pred_df["s2_check_num_het", s2_check_num_het_preds] <- 1

pred_df["s1_check_num_lin", s1_check_num_lin_preds] <- 1
pred_df["s2_check_num_lin", s2_check_num_lin_preds] <- 1

pred_df["s1_check_num_ind", s1_check_num_ind_preds] <- 1
pred_df["s2_check_num_ind", s2_check_num_ind_preds] <- 1

pred_df["s1_check_num_out", s1_check_num_out_preds] <- 1
pred_df["s2_check_num_out", s2_check_num_out_preds] <- 1

pred_df["s1_check_num_inf", s1_check_num_inf_preds] <- 1
pred_df["s2_check_num_inf", s2_check_num_inf_preds] <- 1
```

##### Additional adjustments 

add predictors to world_rank, ri_subfield and demo_level

```{r}
pred_df["world_rank",  c("rank_cat", "recruitment", "ri_subfield")] <- 1

pred_df["ri_subfield", ] <- 0
pred_df["ri_subfield",  c("rank_cat", "demo_level", 
                          "ri_teach",
                          "s1_check_sum", 
                          "s2_check_sum", 
                          "tf_overall_mean" 
                          )] <- 1


pred_df["demo_level",  c("rank_cat", "recruitment", "ri_subfield", "ri_preferred_ht")] <- 1

pred_df["ri_teach", ] <- 0
pred_df["ri_teach",  c("rank_cat", "demo_level", "ri_subfield", "ri_preferred_ht")] <- 1
```


Passively imputed variables should not predict the variables they are imputed from:

```{r}
pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df,
                               dplyr_select_query_col = "'s1_check_sum'",
                               dplyr_select_query_row = "contains('s1_check')",
                               assign = 0)

pred_df <- batch_adjust_matrix(predictor_matrix_df = pred_df,
                               dplyr_select_query_col = "'s2_check_sum'",
                               dplyr_select_query_row = "contains('s2_check')",
                               assign = 0)
```

## Impute data 

```{r}
pred_df[ ,"id"] <- 0
pred_df[ "id",] <- 0
for(i in 1:ncol(pred_df)) pred_df[i, i] <- 0

#pred_df = pred_df[1:135, 1:135]

pred_matrix <- pred_df %>% as.matrix()

set.seed(4)

imputed_data <- mice::mice(data = model_data, 
                           m = 11,
                           method = pred_method, 
                           predictorMatrix = pred_matrix, 
                           visitSequence = "revmonotone",
                           printFlag = FALSE)

```

## Diagnostic plots

#### world_rank

```{r}
mice::densityplot(x = imputed_data, data = ~world_rank)
```

#### ri_teach

```{r}
mice::densityplot(x = imputed_data, data = ~ri_teach)
```

#### ri_subfield

```{r}
mice::densityplot(x = imputed_data, data = ~ri_subfield)
```


#### s1_check_sum

```{r}
mice::densityplot(x = imputed_data, data = ~s1_check_sum)
mice::densityplot(x = imputed_data, data = ~s1_check_num_norm_sam)
mice::densityplot(x = imputed_data, data = ~s1_check_num_norm_err)
mice::densityplot(x = imputed_data, data = ~s1_check_num_het)
mice::densityplot(x = imputed_data, data = ~s1_check_num_out)
mice::densityplot(x = imputed_data, data = ~s1_check_num_inf)
```

#### s2_check_sum

```{r}
mice::densityplot(x = imputed_data, data = ~s2_check_sum)
mice::densityplot(x = imputed_data, data = ~s2_check_num_norm_sam)
mice::densityplot(x = imputed_data, data = ~s2_check_num_norm_err)
mice::densityplot(x = imputed_data, data = ~s2_check_num_het)
mice::densityplot(x = imputed_data, data = ~s2_check_num_out)
mice::densityplot(x = imputed_data, data = ~s2_check_num_inf)
```


# Compute FMI

```{r}

imputed_data_long <- mice::complete(imputed_data, "long", include = TRUE)

imputed_data_s1 <- imputed_data_long %>%
  dplyr::select(.imp:tf_out_inf_50, methods_select_1:tf_out_inf_mean, contains("s1")) %>% 
  dplyr::mutate(scenario = "s1")


imputed_data_s2 <- imputed_data_long %>%
  dplyr::select(.imp:tf_out_inf_50, methods_select_1:tf_out_inf_mean, contains("s2")) %>% 
  dplyr::mutate(scenario = "s2")

names(imputed_data_s1) <- stringr::str_remove_all(pattern = "s1_", string = names(imputed_data_s1))
names(imputed_data_s2) <- stringr::str_remove_all(pattern = "s2_", string = names(imputed_data_s2))

imp_data_long <- rbind.data.frame(imputed_data_s1, imputed_data_s2)

imp_data_long %<>%
  dplyr::mutate(
    across(
      .cols = check_num_lin:check_num_norm_err,
      .fns = ~factor(., ordered = TRUE)
    ), 
    # uni_rank_cat = case_when( # this was computed based on the original imputed variable. uni_rank_cat from this code was used in the models and can be found in the dataset used in the `analysis_models.Rmd` script. 
    #   world_rank == 1500 ~ 4, 
    #   world_rank %in% c(501:1001) ~ 3,
    #   world_rank %in% c(201:500) ~ 2,
    #   world_rank %in% c(1:200) ~ 1
    # ) %>% factor(.), 
    uni_rank_cat = rank_cat %>% factor(.), 
    ri_subfield = factor(ri_subfield, 
                         labels = c("Methods", "Biological", "Clinical", "Cognitive", "Developmental", "Social")),
    row_names = rownames(.)
  ) %>%
  dplyr::group_by(.imp) %>%
  dplyr::mutate(.id = 1:max(row_number())) %>% 
  dplyr::ungroup() 

imp_data_list <- split(imp_data_long, f = imp_data_long$.imp)


m = length(imp_data_list)-1

q = c()
for(i in 2:m){
  q = c(q, median(imp_data_list[[i]]$world_rank, na.rm = T))
}

Vb = sum((q - mean(q))^2) / (m - 1)

Ubi = c()
for(i in 2:m){
  Ubi = c(Ubi, var(imp_data_list[[i]]$world_rank, na.rm = T))
}

Ub = sum(Ubi) / m

Vt = Ub + Vb + Vb/m

r = ((1 + 1/m) * Vb) / Ub

n = nrow(imp_data_list[[1]])

fmi_inf = (Vb + Vb/m) / Vt # fmi formula assuming infinite imputations

v = (m - 1)*(1/fmi_inf) # degrees of freedom for fmi adjustment 
  
fmi = (Vb + Vb/m + 2/(v + 3)) / Vt

fmi/0.01 * 100

fmi/m 

fmi/m <= 0.01


```

Initial m = 30: 

